---
title: "ManyLabs2 - Data HowTo"
author: "(Corresponding coder: [Fred Hasselman](http://fredhasselman.com))"
date: "6 februari 2015"
output:
  html_document:
    highlight: pygments
    theme: cosmo
    toc: yes
  pdf_document: default
  word_document: default
---
```{r set-options, echo=FALSE,include=FALSE}
require(knitr)
require(formatR)
options(width=80)
knitr::opts_chunk$set(cache=TRUE,comment="",message=FALSE,echo=TRUE,warning=FALSE,tidy=TRUE,strip.white=TRUE,size="small")
```
[ManyLabs2](https://osf.io/8cd4r) Data Merge
==================================================

Before we can do anything, you'll need to install some things:
```{r funlib,echo=FALSE}
require(devtools)
source_url(url = 'https://raw.githubusercontent.com/FredHasselman/manylabRs/master/R/ML2_variable_functions.R')
```

Function `inIT` will load and -if necessary- install packages passed in a list (`unIT` will do the reverse operation).
Let's initialise some libraries.
```{r libs,eval=FALSE}
inIT(c("plyr","dplyr","MBESS","metafor","xlsx","hypergeo"))
```

Set the working directory to where the `.csv` files are.
If your dropbox is in your home folder and you copied the `Manylabs2/Raw Data/` folder to your Dropbox, the line below should work.
We'll put the filenames ending in `.csv` in a list object `fileList` (using `grepl` to get a True / False index for the file-extension)
```{r data0,eval=FALSE}
setwd("~/Dropbox/Manylabs2/Raw Data/")
fileList <- dir()[grepl(".csv",dir())]
```

Slate 1
```{r data1,eval=FALSE}
# Merge Slate 1
skip<-list()
ML2.files.S1 <- fileList[grepl("Slate1",fileList)&!(fileList%in%skip)]
names(ML2.files.S1) <- ML2.files.S1
ML2.S1 <- ldply(.data=ML2.files.S1, .fun=get.CSVdata, .inform=T)
# Filter test trials
ML2.S1 <- filter(ML2.S1,!(grepl("test",ML2.S1$age,ignore.case = T)))
```

Slate 2
```{r data2,eval=FALSE}
# Merge Slate 2
skip<-list()
ML2.files.S2 <- fileList[grepl("Slate2",fileList)&!(fileList%in%skip)]
names(ML2.files.S2) <- ML2.files.S2
ML2.S2 <- ldply(.data=ML2.files.S2, .fun=get.CSVdata, .inform=T)
# Filter test trials
ML2.S2 <- filter(ML2.S2,!(grepl("(test)+",ML2.S2$age,ignore.case = T, perl=T)))
```


Save data as `xlsx`, `csv` and `Rds`
```{r data3,eval=FALSE}
# SAVE DATA ---------------------------------------------------------------

# Generate some stats about the datafiles and save to a workbook
setwd("~/Dropbox/Manylabs2/Raw Data")
ML2.vars.S1 <- llply(.data=ML2.files.S1, get.CSVinfo)
ML2.vars.S2 <- llply(.data=ML2.files.S2, get.CSVinfo)

setwd("~/Dropbox/Manylabs2/")
wb    <- createWorkbook()
sheet <- createSheet(wb,sheetName="N per site Slate 1")
addDataFrame(ldply(ML2.vars.S1,function(inf) inf$Info), sheet)
sheet <- createSheet(wb,sheetName="N per site Slate 2")
addDataFrame(ldply(ML2.vars.S2,function(inf) inf$Info), sheet)
saveWorkbook(wb, "ML2_DataFileInfo.xlsx") 

# Raw Data Slate 1 .xlsx, .csv, RDS
write.csv(ML2.S1,"ML2_RawData_S1.csv")
saveRDS(ML2.S1,"ML2_RawData_S1.rds")

# Raw Data Slate 2 .xlsx, .csv, RDS
write.csv(ML2.S2,"ML2_RawData_S2.csv")
saveRDS(ML2.S2,"ML2_RawData_S2.rds")
```

