---
title: "ManLabs2 Original Efects"
author: "Document Author"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

## Effects 

```{r, include=FALSE}
require(devtools)
#srcDir <- "https://raw.githubusercontent.com/FredHasselman/ManyLabRs/master/manylabRs/R/"
srcDir <- "~/Library/Mobile Documents/com~apple~CloudDocs/GitHub/ManyLabRs/manyLabRs/R/"

source(paste0(srcDir,"C-3PR_ASCII.R"))
source(paste0(srcDir,'getData.R'))
source(paste0(srcDir,'inIT.R'))
source(paste0(srcDir,'ML2_variable_functions.R'))
source(paste0(srcDir,'fRedsRutils.R'))

# Function inIT will load and -if necessary- install packages passed in a list (unIT will do the reverse operation).
in.IT(c("MBESS","plyr","dplyr","metafor","RCurl","xlsx","broom","reshape2","httr","compute.es","downloader","car", "lme4", "lmerTest","exact2x2"))

in.IT(c("ggplot2","lattice","latticeExtra"))


ML2.key <- get.GoogleSheet(data='ML2masteRkey')$df
```


```{r, echo=FALSE}
knitr::kable(ML2.key[nchar(ML2.key$orig.stat.type)>0, c(2:5,22:25,28)], booktabs=TRUE, align = "c")
```


## Your Familiar Tools

Feel free to use the `knitr` infrastructure with dozens of tunable options in
your document.

```{r fig.width=6, fig.height=6, fig.align='center'}
set.seed(123)
n <- 1000
x1  <- matrix(rnorm(n), ncol = 2)
x2  <- matrix(rnorm(n, mean = 3, sd = 1.5), ncol = 2)
x   <- rbind(x1, x2)
head(x)
smoothScatter(x, xlab = "x1", ylab = "x2")
```

You can include code snippets of languages other than R, but note that
the block header has no curly brackets around the language name.

```cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can also write math expressions, e.g. $Y = X\beta + \epsilon$,
footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

## Stay Tuned

Please visit the [development page](http://github.com/yixuan/prettydoc/) of the 
`prettydoc` package for latest updates and news. Comments, bug reports and
pull requests are always welcome.
